---
title: "Geom hurricane tutorial"
author: "Coursera Learner 42"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Geom hurricane tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This package provides a geom_hurricane method to be used in ggplot2 to draw hurricanes. It also provides a number of function to interact with hurricane data

```{r, echo=FALSE}
library(CourseraRdataVisualizationFinal)
library(magrittr)
library(ggplot2)
options(width = 120)
```

## Read the hurricane data to a tidy data frame

The whole dataset can be read with the `read_storm_data` method

```{r message=FALSE}
storm_data <- read_storm_data()
print.data.frame(head(storm_data))
```

From there, we can extract the Katrina wind data at the desired observation:

```{r message=FALSE}
katrina <- storm_data %>%
  dplyr::filter(storm_id == 'Katrina-2005' & date == lubridate::ymd_hm("2005-08-29 12:00"))
print.data.frame(katrina)
```

## Helper to create the polygon
```{r}
polygon <- polygon_points(-89.6,29.5,200,100,200,150)
ggplot(polygon, aes(x = lat, y = lon)) +
  geom_polygon()
```



## Example of hurricane illustration with `geom_hurricane`

Draw the katrina observation on the screen:
